Title Goes Here

### 2019-03-29 analysis/paper/paper.Rmd
add spatial plot

```{r get-data, eval = FALSE}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition == 'complete',
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

# plot for intact agate bead by period
ornaments_intact_agate <-
  ornaments_period %>% 
  filter(Condition == c('complete','near-complete'),
         Categories == 'Agate bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

>>>>

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

# plot for intact glass bead by period
ornaments_intact_glass <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Glass bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

# plot for intact agate bead by period
ornaments_intact_agate <-
  ornaments_period %>% 
  filter(Condition %in% c('complete','near-complete'),
         Categories == 'Agate bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

```{r plot-count-type-by-period}
# plot for different shape of agate bead by period
agate_bead_shape <-
  ornaments_period %>% 
  filter(Categories == 'Agate bead') %>% 
  mutate(Type = ifelse(Type == 'prism/octagonal', 
                       str_remove(Type, '/octagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/pentagonal', 
                       str_remove(Type, '/pentagonal'), Type)) %>% 
  mutate(Type = ifelse(Type == 'prism/hexagonal', 
                       str_remove(Type, 'prism/'), Type)) %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

ggplot(transform(agate_bead_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Agate bead") +
  theme_minimal(base_size = 14)

# plot for different shape of metal bell by period
bell_shape <-
  ornaments_period %>% 
  filter(Categories == 'Bell',
         Type != 'unclassified') %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

ggplot(transform(bell_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Bell") +
  theme_minimal(base_size = 14)

# plot for different shape of metal ring by period
ring_shape <-
  ornaments_period %>% 
  filter(Categories == 'Metal ring') %>% 
  mutate(Type = fct_infreq(Type)) %>% 
  mutate(Type = fct_rev(Type)) %>% 
  group_by(period, Type) %>% 
  count()

ggplot(transform(ring_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Metal ring") +
  theme_minimal(base_size = 14)
```

```{r scatter-plot-metal-by-period}
# plot for intact bell by period
ornaments_intact_bell <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Bell',
         Type != 'unclassified') %>% 
  mutate(Length = as.numeric(gsub("\\+", "", `Length(mm)`)), #remove +
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`))

ggplot(transform(ornaments_intact_bell,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Bell") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

# plot for intact ring by period
ornaments_intact_ring <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Metal ring') %>% 
  mutate(Length = as.numeric(gsub("\\+|\\-", "", `Length(mm)`)), #remove + -
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`))

ggplot(transform(ornaments_intact_ring,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Metal ring") +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))
```

```{r read-in-the-spatial-data, eval = FALSE}
library(sf)
library(cartography)
burial <- st_read(here("analysis", "data", "raw_data", "AD_burial.shp"))
AD <- st_read(here("analysis", "data", "raw_data", "AD_zone.shp"))
AD_data <- st_read(here("analysis", "data", "raw_data", "AD_withdata.shp"))
location <- st_read(here("analysis", "data", "raw_data", "location.shp"))
units_40 <- read.csv(here("analysis", "data", "raw_data", "kwl-list-of-sampling-squares.csv"))
```

```{r tidy-data, eval = FALSE}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))

# join two dataset to get coordinate
ornaments_period_join <-
  ornaments_period %>%
  mutate(period = as.factor(period)) %>% # seems need this line first 
  group_by(Pit_No, period) %>% 
  count(Categories) %>% 
  inner_join(AD_data, by = c("Pit_No" = "坑號"))

# filter golden bead
ornaments_period_join_gold <-
  ornaments_period_join %>% 
  filter(Categories %in% 'Golden bead')

# plot by period
ggplot(transform(ornaments_period_join_gold,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_sf(data = sample_units) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n)) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Golden Beads",
       fill = "frequency") +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank())
```
